Statistical Machine Learning Models on A Bank Marketing dataset

### 2025-12-08 Slides.Rmd
correct path

```{r slide2-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("imbalance_plot.png")
```

@@

```{r eda1-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("contact_plot.png")

@@

```{r eda2-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("poutcome_plot.png")
```

@@

```{r eda3-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("campaign_plot.png")
```

>>>>

```{r slide2-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/imbalance_plot.png")
```

@@

```{r eda1-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/contact_plot.png")

@@

```{r eda2-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/poutcome_plot.png")
```

@@

```{r eda3-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/campaign_plot.png")
```
